---
title: "Homework 1"
output: github_document
---

```{r setup}
library(tidyverse)

set.seed(1)
```

## Problem 1

Creating a data frame that has 10 subjects randomly sampled from a standard Normal distribution, a logical vector indicating whether these values are greater than 0, a corresponding character vector, and a factor vector with 3 different levels. 

```{r}
P1_df = tibble(
  norm_samp = rnorm(10, mean = 0, sd = 1),
  norm_samp_pos = norm_samp > 0, 
  chr_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  fct_vec = factor(c("red", "blue", "yellow", "blue", "red", "red", "yellow", "blue", "red", "yellow"))
)
```

Taking the mean of each variable: 

```{r}
num = pull(P1_df, norm_samp)
logi = pull(P1_df, norm_samp_pos)
chr = pull(P1_df, chr_vec)
fct = pull(P1_df, fct_vec)

mean(num)
mean(logi)
mean(chr)
mean(fct)
```

mean() works for the numeric and logical vectors, while it does not work for character and factor vectors.
Taking averages for numbers and logical vector (TRUE as 1 and FALSE as 0) is doable, while it is not reasonable to get means of characters and factors. 

```{r, eval = FALSE}
num_logi = as.numeric(logi)
num_chr = as.numeric(chr)
num_fct = as.numeric(fct)
```

The logical and factor vectors are successfully transformed into numeric vectors, while the character vector fails to do so. For the logical vector, TRUE and FALSE are assigned values 1 and 0; for the factor vectors, the three factor levels are assigned 1, 2, and 3 as values. However, the ten characters are distinct and cannot be assigned numeric values. Thus, we cannot take average of character vector since it cannot be representated by numeric values. 

